---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(HW3.625)
library(NHANES)
library(Hmisc)
library(bench)
library(datasets)
```

# Package work flow

We use the data set NHANES as a example to show how to use this package.

```{r}
#Looking at the NHANES data set
head(NHANES)
```

First we fit the model using linear().  

Here we use input information "BPSysAve", "SleepHrsNight BMI Age" and NHANES to three function as the test model.  
```{r}
b_l <- basic_linear("BPSysAve","SleepHrsNight BMI Age",NHANES)
l_E <- l_Estimation(b_l[[3]],b_l[[2]],b_l[[6]],b_l[[7]],b_l[[4]],b_l[[5]])
l_s <- l_stat(l_E[[1]],l_E[[5]],l_E[[6]],l_E[[7]],
              b_l[[6]],b_l[[7]],b_l[[2]])

```

Next we use those variables to *summary_linear* to generate the results\  

```{r}
summary_linear(b_l,l_E,l_s)
```

# Test cases

## SLR - variable is continous
```{r}
slr_bl <- basic_linear("BPSysAve","Age",NHANES)

slr_le <- l_Estimation(slr_bl[[3]],slr_bl[[2]],slr_bl[[6]],
                    slr_bl[[7]],slr_bl[[4]],slr_bl[[5]])

slr_ls <- l_stat(slr_le[[1]],slr_le[[5]],slr_le[[6]],slr_le[[7]],
              slr_bl[[6]],slr_bl[[7]],slr_bl[[2]])

summary_linear(slr_bl,slr_le,slr_ls)
```

## SLR - variable is continous
```{r}
model_slr <- lm(BPSysAve~Age,NHANES)
summary(model_slr)
```


## MLR - variables are all continous
```{r}
mlr_bl <- basic_linear("BPSysAve","SleepHrsNight BMI Age",NHANES)
mlr_le <- l_Estimation(mlr_bl[[3]],mlr_bl[[2]],mlr_bl[[6]],
                      mlr_bl[[7]],mlr_bl[[4]],mlr_bl[[5]])
mlr_ls <- l_stat(mlr_le[[1]],mlr_le[[5]],mlr_le[[6]],mlr_le[[7]],
              mlr_bl[[6]],mlr_bl[[7]],mlr_bl[[2]])
summary_linear(mlr_bl,mlr_le,mlr_ls)
```

```{r}
model_mlr <- lm(BPSysAve~SleepHrsNight+BMI+Age,NHANES)
summary(model_mlr)
```


# Comparing linear() with exsiting function lm() 

```{r}
model_test1 <- mlr_le 
model_test2 <- mlr_ls 
```

```{r}
#Fitted model using lm()
model_refer <- model_mlr
```

Checking the coefficient estimates

```{r}
all.equal(as.numeric(model_test1[[1]]),as.numeric(model_refer$coefficients))
```

Checking the confident interval of linear is the right answer.

```{r}
all.equal(as.numeric(model_test2[[6]]),as.numeric(confint(model_refer)[,1]))
```

```{r}
all.equal(as.numeric(model_test2[[7]]),as.numeric(confint(model_refer)[,2]))
```

# Comparing summary_blog() with summary() from the base R
```{r}
#Between the same model fitted using lm_blog()
summary(model_mlr)
```

```{r}
summary_linear(mlr_bl,mlr_le,mlr_ls)
```

#Efficiency test
```{r}
data(iris)
b_l <- basic_linear("Sepal.Length", "Sepal.Width Petal.Length",iris)
l_E <- l_Estimation(b_l[[3]],b_l[[2]],b_l[[6]],b_l[[7]],b_l[[4]],b_l[[5]])
l_s <- l_stat(l_E[[1]],l_E[[5]],l_E[[6]],l_E[[7]],b_l[[6]],b_l[[7]],b_l[[2]])
model <- lm(Sepal.Length~Sepal.Width+Petal.Length,data=iris)
model_refer2 <- confint(model)
system.time(basic_linear("Sepal.Length", "Sepal.Width Petal.Length",iris))
```

```{r}
system.time(l_Estimation(b_l[[3]],b_l[[2]],b_l[[6]],b_l[[7]],b_l[[4]],b_l[[5]]))
```

```{r}
system.time(l_stat(l_E[[1]],l_E[[5]],l_E[[6]],l_E[[7]],b_l[[6]],b_l[[7]],b_l[[2]]))
```

```{r}
system.time(summary_linear(b_l,l_E,l_s))
```

```{r}
#This is the time costed by exsiting function
system.time(lm(Sepal.Length~Sepal.Width+Petal.Length,data=iris))
```

```{r}
system.time(summary(model))
```

```{r}
result <- bench::mark(as.numeric(model_test1[[1]]),as.numeric(model_refer$coefficients))
print(result)
```
